---
title: "philosophy data story"
author: "Yunfan LIu yl5111"
date: '2023-01-19'
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Step 0: Load Libraries and Data Set
```{r}
library(dplyr)
library(vistime)
library(lubridate)
library(plotly)
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(wordcloud2)
```

If R cannot open the file, please go to README.md under data folder, and 
download philosophy_data.csv from the link. This happens because the csv file
is over 300 MB.

Load Data
```{r}
pdata= read.csv(file="../data/philosophy_data.csv",header=TRUE)
head(pdata)
```


## Q1: How many philosophers? Who are they?
Since the data set is big and new to me, and it seems many rows have the 
same author. First, let's see how many philosophers are there, and who are they?

```{r}
unique(pdata$author)
```

```{r}
length(unique(pdata$author))
```
So, in our data set, we have 36 different philosophers.


## Q2: How many sentences each philosopher said? Who said the most sentences?
Since the data set is about the maxims those philosophers said, I am wondering
how many sentences each philosopher said in their life time, and who is the
most long-winded philosopher?

First, I build a new data frame which counts the number of sentences each 
philosopher said, it's called author_count.

Then, I choose to visualize the result in a bar graph. Due to limited space, 
each philosopher is represented by the first 3 letters of his name.

```{r}
author_count = pdata %>% group_by(author) %>% summarise(total_count=n(),
            .groups = 'drop')
head(author_count)
```


```{r}
author_3=list()
for (i in author_count$author){
  author_3=append(author_3,substr(toString(i),1,3))}
```
```{r}
barplot(author_count$total_count,col=rainbow(36),width=4,
        names.arg=author_3,
        cex.names=0.25,space=4, cex.axis=0.7) 
```

Aristotle said the most maxims, with over 40000 sentences.


## Q3: How many shcools do they have? Which school has the most philosophers supported?
I noticed that the data set also provides school information. I am wondering how 
many schools are there in this data set, and which school is the most powerful?

I start to build a data frame called school_count, which counts the number of 
philosophers in each school.

I choose to visualize the result in a pie chart.

```{r}
unique(pdata$school)
```
```{r}
school_count = pdata %>% group_by(school) %>% summarise(
  num_of_author=n_distinct(author),.groups = "drop")
head(school_count)
```
```{r}
pct <- round(school_count$num_of_author/sum(school_count$num_of_author)*100)
lables <- school_count$school
lables = paste(lables, pct)
lables <- paste(lables,"%",sep="")
pie(school_count$num_of_author, labels =lables, main="PIE FOR SCHOOL",cex=0.9)
```

It is clear that most philosophers are in analytic school.


## Q4: How did schools develop?
Since I explored the schools, and found out their appeal towards philosophers.
I think one reason for the difference in number of supporters is time, for 
example, some schools developed earlier. So, i want to show a time line about
philosophy school development.

```{r}
school_time = pdata %>% group_by(school) %>% summarise(original_publication_date,
            .groups = 'drop')
school_time= school_time %>% distinct()
school_time= school_time %>% arrange(original_publication_date)
head(school_time)
```

```{r}
## transfer integer year into date type
start_i=c(125,1637,1689,1776,1781,1792,1848,1886,1907,1910,1961)

start_1=as.Date(ISOdate(start_i, 1, 1)) 
a= c(make_date(year = -350L),make_date(year = -320L))

start=c(a,start_1)

end_i= c(170,1710,1779,1936,1820,1981,1883,1888,1950,1985,1972)
end_1= as.Date(ISOdate(end_i, 1, 1))
b= c(make_date(year = -350L),make_date(year = -320L))
end= c(b,end_1)

```

```{r}
timedata= data.frame(event= unique(school_time$school),
                    start= start,
                    end= end)
gg_vistime(timedata,
           optimize_y = FALSE,
           linewidth = 8,
           show_labels=TRUE,
           background_lines=3,
           title="Philosophy Development"
           )

```

Although the data set says all Plato and Aristotle sentences were in 350 and 
320 B.C., it does not mean that the 2 schools ended and there were no philosophy 
in medieval Age.I did some research and found out that Plato and Aristotle 
were the two leading influences on medieval thought.


## Q5: What is the general topic for all philosophers? For each school?

I would like to know what is the biggest topic of philosophy from ancient times 
to modern times. I remove the pointless words like "one, can, will, things..."

Actually, before i remove the pointless words, guess what is the most common
word in philosophy? I thought it would be "the", or "is, are", but it is "one". Philosophers love to use "one" as subject, for example, they would say 
"One is ...".
I am curious about how many sentences have "one".

# How many maxims have "one"?
```{r}
count=0
for (i in pdata$sentence_lowered){
  if (grepl("one",i,fixed=TRUE)){
    count=count+1
  }
}
(count/nrow(pdata))*100
```

16.95722% of maxims have "one".


# Common Word ALL Philosophers
```{r}
text_all = removePunctuation(pdata$sentence_lowered)

text_all= gsub("one","",text_all)
text_all= gsub("can",'',text_all)
text_all= gsub("must",'',text_all)
text_all= gsub("will",'',text_all)
text_all= gsub("may",'',text_all)
text_all= gsub("things",'',text_all)
text_all= gsub("thing",'',text_all)
text_all= gsub("also",'',text_all)
text_all= gsub("even",'',text_all)
text_all= gsub("therefore",'',text_all)
text_all= gsub("say",'',text_all)
text_all= gsub("said",'',text_all)
text_all= gsub("just",'',text_all)
text_all= gsub("man",'',text_all)
text_all= gsub("every",'',text_all)

wordcloud(text_all, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE
        , colors=brewer.pal(8, "Dark2"))


```



# By School


Analytic
```{r}
df_anal =pdata[pdata$school =='analytic',]

text_anal = removePunctuation(df_anal$sentence_lowered)
text_anal= gsub("one","",text_anal)
text_anal= gsub("can",'',text_anal)
text_anal= gsub("must",'',text_anal)
text_anal= gsub("will",'',text_anal)
text_anal= gsub("may",'',text_anal)
text_anal= gsub("things",'',text_anal)
text_anal= gsub("thing",'',text_anal)
text_anal= gsub("also",'',text_anal)
text_anal= gsub("even",'',text_anal)
text_anal= gsub("therefore",'',text_anal)
text_anal= gsub("say",'',text_anal)
text_anal= gsub("said",'',text_anal)
text_anal= gsub("just",'',text_anal)
text_anal= gsub("man",'',text_anal)
text_anal= gsub("every",'',text_anal)


wordcloud(text_anal, scale=c(3,0.4), max.words=250, random.order=FALSE, 
          rot.per=0.5       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))


```


Plato
```{r}
df_plato =pdata[pdata$school =='plato',]

text_plato = removePunctuation(df_plato$sentence_lowered)

text_plato= gsub("one","",text_plato)
text_plato= gsub("can",'',text_plato)
text_plato= gsub("must",'',text_plato)
text_plato= gsub("will",'',text_plato)
text_plato= gsub("may",'',text_plato)
text_plato= gsub("things",'',text_plato)
text_plato= gsub("thing",'',text_plato)
text_plato= gsub("also",'',text_plato)
text_plato= gsub("even",'',text_plato)
text_plato= gsub("therefore",'',text_plato)
text_plato= gsub("say",'',text_plato)
text_plato= gsub("said",'',text_plato)
text_plato= gsub("just",'',text_plato)
text_plato= gsub("man",'',text_plato)
text_plato= gsub("every",'',text_plato)

wordcloud(text_plato, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```


Aristotle
```{r}
df_aristotle =pdata[pdata$school == 'aristotle',]

text_aristotle = removePunctuation(df_aristotle$sentence_lowered)

text_aristotle= gsub("one","",text_aristotle)
text_aristotle= gsub("can",'',text_aristotle)
text_aristotle= gsub("must",'',text_aristotle)
text_aristotle= gsub("will",'',text_aristotle)
text_aristotle= gsub("may",'',text_aristotle)
text_aristotle= gsub("things",'',text_aristotle)
text_aristotle= gsub("thing",'',text_aristotle)
text_aristotle= gsub("also",'',text_aristotle)
text_aristotle= gsub("even",'',text_aristotle)
text_aristotle= gsub("therefore",'',text_aristotle)
text_aristotle= gsub("say",'',text_aristotle)
text_aristotle= gsub("said",'',text_aristotle)
text_aristotle= gsub("just",'',text_aristotle)
text_aristotle= gsub("man",'',text_aristotle)
text_aristotle= gsub("every",'',text_aristotle)


wordcloud(text_aristotle, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```


Capitalism
```{r}
df_capitalism =pdata[pdata$school == 'capitalism',]

text_capitalism = removePunctuation(df_aristotle$sentence_lowered)

text_capitalism= gsub("one","",text_capitalism)
text_capitalism= gsub("can",'',text_capitalism)
text_capitalism= gsub("must",'',text_capitalism)
text_capitalism= gsub("will",'',text_capitalism)
text_capitalism= gsub("may",'',text_capitalism)
text_capitalism= gsub("things",'',text_capitalism)
text_capitalism= gsub("thing",'',text_capitalism)
text_capitalism= gsub("also",'',text_capitalism)
text_capitalism= gsub("even",'',text_capitalism)
text_capitalism= gsub("therefore",'',text_capitalism)
text_capitalism= gsub("say",'',text_capitalism)
text_capitalism= gsub("said",'',text_capitalism)
text_capitalism= gsub("just",'',text_capitalism)
text_capitalism= gsub("man",'',text_capitalism)
text_capitalism= gsub("every",'',text_capitalism)


wordcloud(text_capitalism, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```

German_idealism
```{r}
df_ger =pdata[pdata$school == 'german_idealism',]

text_ger = removePunctuation(df_ger$sentence_lowered)

text_ger= gsub("one","",text_ger)
text_ger= gsub("can",'',text_ger)
text_ger= gsub("must",'',text_ger)
text_ger= gsub("will",'',text_ger)
text_ger= gsub("may",'',text_ger)
text_ger= gsub("things",'',text_ger)
text_ger= gsub("thing",'',text_ger)
text_ger= gsub("also",'',text_ger)
text_ger= gsub("even",'',text_ger)
text_ger= gsub("therefore",'',text_ger)
text_ger= gsub("say",'',text_ger)
text_ger= gsub("said",'',text_ger)
text_ger= gsub("just",'',text_ger)
text_ger= gsub("man",'',text_ger)
text_ger= gsub("every",'',text_ger)


wordcloud(text_ger, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```


Continental
```{r}
df_con =pdata[pdata$school == 'continental',]

text_con = removePunctuation(df_con$sentence_lowered)

text_con= gsub("one","",text_con)
text_con= gsub("can",'',text_con)
text_con= gsub("must",'',text_con)
text_con= gsub("will",'',text_con)
text_con= gsub("may",'',text_con)
text_con= gsub("things",'',text_con)
text_con= gsub("thing",'',text_con)
text_con= gsub("also",'',text_con)
text_con= gsub("even",'',text_con)
text_con= gsub("therefore",'',text_con)
text_con= gsub("say",'',text_con)
text_con= gsub("said",'',text_con)
text_con= gsub("just",'',text_con)
text_con= gsub("man",'',text_con)
text_con= gsub("every",'',text_con)


wordcloud(text_con, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```


Empiricism
```{r}
df_emp =pdata[pdata$school == 'empiricism',]

text_emp = removePunctuation(df_emp$sentence_lowered)

text_emp= gsub("one","",text_emp)
text_emp= gsub("can",'',text_emp)
text_emp= gsub("must",'',text_emp)
text_emp= gsub("will",'',text_emp)
text_emp= gsub("may",'',text_emp)
text_emp= gsub("things",'',text_emp)
text_emp= gsub("thing",'',text_emp)
text_emp= gsub("also",'',text_emp)
text_emp= gsub("even",'',text_emp)
text_emp= gsub("therefore",'',text_emp)
text_emp= gsub("say",'',text_emp)
text_emp= gsub("said",'',text_emp)
text_emp= gsub("just",'',text_emp)
text_emp= gsub("man",'',text_emp)
text_emp= gsub("every",'',text_emp)


wordcloud(text_emp, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```

Rationalism
```{r}
df_rat =pdata[pdata$school == 'rationalism',]

text_rat = removePunctuation(df_rat$sentence_lowered)

text_rat= gsub("one","",text_rat)
text_rat= gsub("can",'',text_rat)
text_rat= gsub("must",'',text_rat)
text_rat= gsub("will",'',text_rat)
text_rat= gsub("may",'',text_rat)
text_rat= gsub("things",'',text_rat)
text_rat= gsub("thing",'',text_rat)
text_rat= gsub("also",'',text_rat)
text_rat= gsub("even",'',text_rat)
text_rat= gsub("therefore",'',text_rat)
text_rat= gsub("say",'',text_rat)
text_rat= gsub("said",'',text_rat)
text_rat= gsub("just",'',text_rat)
text_rat= gsub("man",'',text_rat)
text_rat= gsub("every",'',text_rat)


wordcloud(text_rat, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```

Phenomenology
```{r}
df_phe =pdata[pdata$school == 'phenomenology',]

text_phe = removePunctuation(df_phe$sentence_lowered)

text_phe= gsub("one","",text_phe)
text_phe= gsub("can",'',text_phe)
text_phe= gsub("must",'',text_phe)
text_phe= gsub("will",'',text_phe)
text_phe= gsub("may",'',text_phe)
text_phe= gsub("things",'',text_phe)
text_phe= gsub("thing",'',text_phe)
text_phe= gsub("also",'',text_phe)
text_phe= gsub("even",'',text_phe)
text_phe= gsub("therefore",'',text_phe)
text_phe= gsub("say",'',text_phe)
text_phe= gsub("said",'',text_phe)
text_phe= gsub("just",'',text_phe)
text_phe= gsub("man",'',text_phe)
text_phe= gsub("every",'',text_phe)


wordcloud(text_phe, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```

Communism
```{r}
df_comm =pdata[pdata$school == 'communism',]

text_comm = removePunctuation(df_comm$sentence_lowered)

text_comm= gsub("one","",text_comm)
text_comm= gsub("can",'',text_comm)
text_comm= gsub("must",'',text_comm)
text_comm= gsub("will",'',text_comm)
text_comm= gsub("may",'',text_comm)
text_comm= gsub("things",'',text_comm)
text_comm= gsub("thing",'',text_comm)
text_comm= gsub("also",'',text_comm)
text_comm= gsub("even",'',text_comm)
text_comm= gsub("therefore",'',text_comm)
text_comm= gsub("say",'',text_comm)
text_comm= gsub("said",'',text_comm)
text_comm= gsub("just",'',text_comm)
text_comm= gsub("man",'',text_comm)
text_comm= gsub("every",'',text_comm)


wordcloud(text_comm, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```

Stoicism
```{r}
df_sto =pdata[pdata$school == 'stoicism',]

text_sto = removePunctuation(df_sto$sentence_lowered)

text_sto= gsub("one","",text_sto)
text_sto= gsub("can",'',text_sto)
text_sto= gsub("must",'',text_sto)
text_sto= gsub("will",'',text_sto)
text_sto= gsub("may",'',text_sto)
text_sto= gsub("things",'',text_sto)
text_sto= gsub("thing",'',text_sto)
text_sto= gsub("also",'',text_sto)
text_sto= gsub("even",'',text_sto)
text_sto= gsub("therefore",'',text_sto)
text_sto= gsub("say",'',text_sto)
text_sto= gsub("said",'',text_sto)
text_sto= gsub("just",'',text_sto)
text_sto= gsub("man",'',text_sto)
text_sto= gsub("every",'',text_sto)


wordcloud(text_sto, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```

* thou means you in old days.

Nietzsche
```{r}
df_nie =pdata[pdata$school == 'nietzsche',]

text_nie = removePunctuation(df_nie$sentence_lowered)

text_nie= gsub("one","",text_nie)
text_nie= gsub("can",'',text_nie)
text_nie= gsub("must",'',text_nie)
text_nie= gsub("will",'',text_nie)
text_nie= gsub("may",'',text_nie)
text_nie= gsub("things",'',text_nie)
text_nie= gsub("thing",'',text_nie)
text_nie= gsub("also",'',text_nie)
text_nie= gsub("even",'',text_nie)
text_nie= gsub("therefore",'',text_nie)
text_nie= gsub("say",'',text_nie)
text_nie= gsub("said",'',text_nie)
text_nie= gsub("just",'',text_nie)
text_nie= gsub("man",'',text_nie)
text_nie= gsub("every",'',text_nie)


wordcloud(text_nie, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```

* Zarathustra is also known as Zoroaster. He is said to have been an Iranian prophet.

Feminism
```{r}
df_fem =pdata[pdata$school == 'feminism',]

text_fem = removePunctuation(df_fem$sentence_lowered)

text_fem= gsub("one","",text_fem)
text_fem= gsub("can",'',text_fem)
text_fem= gsub("must",'',text_fem)
text_fem= gsub("will",'',text_fem)
text_fem= gsub("may",'',text_fem)
text_fem= gsub("things",'',text_fem)
text_fem= gsub("thing",'',text_fem)
text_fem= gsub("also",'',text_fem)
text_fem= gsub("even",'',text_fem)
text_fem= gsub("therefore",'',text_fem)
text_fem= gsub("say",'',text_fem)
text_fem= gsub("said",'',text_fem)
text_fem= gsub("just",'',text_fem)
text_fem= gsub("man",'',text_fem)
text_fem= gsub("every",'',text_fem)


wordcloud(text_fem, scale=c(3,0.2), max.words=250, random.order=FALSE, 
          rot.per=0.35       
        , use.r.layout=TRUE 
        , colors=brewer.pal(8, "Dark2"))
```

## Conclusion
1. Aristotle said the largest amount of maxims, with over 40000 sentences.
2. Analytic has 19% of philosophers, other schools have almost the same amount
of supporters.













